Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2019-11-20 awipev-CO2.Rmd

<!--The slope is: `r at_slope_TA1` x 3600 x 24 x 365.24 = `r at_slope1` µmoles.kg-1.yr-1. Regression is: R2 = `r round(signif(summary(fit)$adj.r.squared, 5), digits =4)`. Outliers are in red.
-->

```{r First period plot, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold', fig.align="center"}
# # Plot of regression
# p <- ggplot(calib_ta_first%>%filter(diff_ta <= 50),aes(datetime,diff_ta)) + 
#     geom_point() + geom_smooth(method='lm', se=FALSE)+ 
#     geom_point(data= calib_ta_first%>%filter(diff_ta >= 50), aes(x=datetime, y=diff_ta), color="red")  +
#   geom_hline(yintercept = 0, linetype="dashed" )+
#   labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
#                      "Intercept =",signif(fit$coef[[1]],5 ),
#                      "Slope =",signif(fit$coef[[2]], 5),
#                      "P =",signif(summary(fit)$coef[2,4], 5))) + 
#   ylab("Difference: Reference - Analyser") + xlab("Time") + scale_x_datetime(date_labels = "%b %Y", date_minor_breaks = "month", timezone="UTC")
# print(p)
# ggsave(paste0("figures/Diff_ref_TA_first_period.png"), p, units="cm")
```

@@

```{r Third period, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold',fig.align="center"}

# #remove outliers and remove period without TA measurements 
# calib_ta_third <- d_all%>%
#   dplyr::select(datetime, closest_datetime,AT_filtered, AT_filtered_interp, at,diff_ta, TA_period)%>%
#   dplyr::filter(TA_period == "TA3" & !is.na(at))
# 
# # Parameters of regression
# fit <- lm( data=calib_ta_third, diff_ta ~ datetime)
# at_slope_TA3 <- round(fit$coefficients[[2]] , digits=8)
# at_slope3 <- round(at_slope_TA3 * 3600 *24 * 365.24, digits=2)
# at_intercept3 <- round(fit$coefficients[[1]], digits= 2) # pas besoin ici.
```

<!--The slope is in days: `r at_slope_TA3` x 3600 x 24 x 365.24 = `r at_slope3` µmoles.kg-1.an-1. Regression is: R2 = `r round(signif(summary(fit)$adj.r.squared, 5), digits =4)`. No outliers.

```{r Third period plot, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold', fig.align="center"}
# # Plot of regression
 p <- ggplot(calib_ta_third,aes(x=datetime, y=diff_ta) )+ 
     geom_point() + geom_smooth(method='lm', se=FALSE)+ 
     #geom_point(data= calib_ta_third%>%filter(diff_ta < -40 & diff_ta<20), aes(x=datetime, y=diff_ta), color="red")  +
    geom_hline(yintercept = 0, linetype="dashed" )+
   geom_vline(xintercept = as.POSIXct("2018-01-08 12:55:00", tz="UTC"), colour="red", linetype = "longdash") +
   #geom_text(aes(xintercept=as.POSIXct("2018-01-01 12:55:00"),label="TA "), colour="red", vjust=1.2)+
   labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                      "Intercept =",signif(fit$coef[[1]],5 ),
                      " Slope =",signif(fit$coef[[2]], 5),
                      " P =",signif(summary(fit)$coef[2,4], 5))) + ylab("Difference: Reference - Analyser") + xlab("Time") + 
   scale_x_datetime( date_labels = "%b %Y", date_minor_breaks = "month", timezone="UTC")
 print(p)
 ggsave(paste0("figures/Diff_ref_TA_third_period.png"), p, units="cm")
```

@@

```{r Second period, echo=FALSE, warning=FALSE, message=FALSE, out.width="100%",fig.show='hold'}

@@

```
For the second period, the average difference between 5 discrete samples "references" and TA analyser measurements (`r mean_offset` µmoles.kg~-1~) was added to TA value as an offset.
-->
<!--
#### **Final TA corrected data (Regression)**

The following plot shows the corrected TA data with regressions (Periods 1 and 3) and with offset (Period 2) applied according to Steffen's proposition.
It is clear that these corrected data (in green) cannot be used for periods 1 to 3. The jury is still out for period 4. The issue of salinity must be clarified before an assessment can be made.

```{r Correction applied, echo=FALSE, warning=FALSE, message=FALSE, out.width="100%",fig.show='hold'}

@@

@@

In the previous part, missing TA were interpolated with a linear model. This does not reflect the natural variability of TA. For this reason, missing TA is now calculated from salinity data by making a relationship between the same reference TA samples as in the previous part and salinity data.

```{r Discrete salinity vs TA, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%", fig.align="center"}
# d_all_at_discrete <- d_all %>% #  To remove an outlier in red 
#   dplyr::select(datetime, month,closest_datetime, at, sal_fb)%>%
#   dplyr::filter( !is.na(at) & !is.na(sal_fb) & sal_fb >30)
#   
#   #at != "2307.05" & sal_fb > 28, !is.na(at))
# 
# # d_all_Out <- d_all %>% #  To keep an outlier in red 
# #   filter(at == "2307.05")
# 
# #fit <- lm(data = drop_na(d_all_at_discrete, at), at ~ sal_fb)
# fit <- lm(data = d_all_at_discrete, at ~ sal_fb)
# slope_s_at <- fit$coefficients[[2]]
# intercept_s_at <- fit$coefficients[[1]]
# # at_s <- ggreg(fit)+ labs(x="Salinity", y="Discrete TA") + Mytheme()
#  
# at_s <- ggplot(d_all_at_discrete,aes(x=sal_fb, y= at, label = month))+
#   geom_text( aes(color=factor(month))) +
#   scale_color_discrete(guide="none")+
#     labs(x="Salinity", y="Discrete AT", color = "Months")  +
#     stat_smooth(method = "lm", col = "black") +
#     labs(title = paste("", "\nAdj R2 = ",signif(summary(fit)$adj.r.squared, 5),
#                        ";\nIntercept =",signif(fit$coef[[1]],5 ),
#                        ";\nSlope =",signif(fit$coef[[2]], 5),
#                        ";\nP =",signif(summary(fit)$coef[2,4], 5))) +
#   theme_bw() + 
#   theme(aspect.ratio=1,
#         axis.text=element_text(size=15),
#         axis.title.y= element_text(size =15),
#         axis.title.x= element_text(size =15),
#         plot.margin = unit(c(0.5,1,1,1), "cm"),
#         plot.title = element_text(size=15, hjust=0.05,margin = margin(l = 10, b = -70))) 
#   #print(at_s)
# 
# ggsave(paste0("figures/Discrete_TA_salinity_AWIPEV.png"), at_s, width=15, height =11, units="cm")
# 
# # Salinity is a predictor of AT -> using the regression defined above
# d_all$at_calc <- slope_s_at * d_all$sal_fb + intercept_s_at
```
The relationship between titrated total alkalinity (references) and salinity is very good with an r2 of `r round(summary(fit)$r.squared, digits=2)`. Need to compare with other relationships from the literature.
-->
```{r plot Discrete salinity vs TA, echo=FALSE, warning=FALSE, message=FALSE, out.width="60%", fig.align="center"}
# # PLOT
# print(at_s)
```

@@

```{r Plot TA calc TA meas, echo=FALSE, warning=FALSE, message=FALSE,out.width='100%',fig.align='hold'}
# at_contros_calc_xts <- dplyr::select(d_all, datetime,at_calc, AT_filtered, at)
# at_contros_calc_xts <-  as.xts(at_contros_calc_xts, order.by =d_all$datetime)
# dygraph(at_contros_calc_xts, group = "awipev", main="", ylab="Total alkalinity") %>%
#   dySeries("AT_filtered", label= "Raw filtered TA", color ="blue", strokeWidth = 0, pointSize=2) %>%
#   dySeries("at_calc", label="TA calculated from Salinity",color = RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize=2) %>%
#   dyAxis("y",valueRange = c(2000, 2650)) %>%
# # #plot for POSTER june 2019
# # #plot of TA calculated from S + discrete
# # p_at_sal <- ggplot(data = d_all%>%dplyr::filter(at_calc > 2000), aes(x=datetime,y=at_calc,col="TA calculated from salinity") ) +
# #   geom_point(col="blue", size=0.5 )+
# #   geom_point(aes(y=at, fill= "Discrete measurements"), col="red") +
# #   labs(title=  "Calculated from salinity (µmol/kg)", x = "", y= "") + ylim(2100,2350)+
# #   theme_bw() + scale_x_datetime(minor_breaks  = "1 month ")+
# #   theme(legend.position= c(0.5, 0.93),
# #                      legend.text=element_text(size=15),
# #                      plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin(t = 9, b = -25)),
# #                      axis.text=element_text(size=15),
# #                      axis.title.x= element_text(size =15),
# #                      legend.title=element_blank())
# # 
# # 
# # print(p_at_sal)
# # ggsave(paste0("figures/poster_at_sal.png"), width= 30, height=10, p_at_sal, units="cm")

@@

#### **TA since November 2018 (final installation)**
```{r TA since November 2018, echo=FALSE, warning=FALSE, message=FALSE,out.width='100%',fig.align='hold'}
# # select subset of data and remove obvious outliers
# at_nov_2018 <- 
#   dplyr::select(d_all, datetime, at_calc, AT_filtered, at) %>%
#   filter(datetime > "2018-11-01", AT_filtered > 2250)
# #despike
# at_nov_2018 <- mutate(at_nov_2018, AT_filtered_despike = despike(AT_filtered, reference= "median", n=0.5, k=10, replace="NA"))
# #plot
# at_datetime <- ggplot(data = at_nov_2018, aes(x=datetime)) +
#   geom_point(aes(y=AT_filtered, colour = "before"), size =3) +
#   geom_point(aes(y=AT_filtered_despike, colour = "after"), size = 2) +
#   labs(x = "Time", y = "Total alkalinity", color = "despike") 
# print(at_datetime)
# 
# at_nov_2018_no_NA <- dplyr::filter(at_nov_2018, at_calc != "NA" & AT_filtered_despike != "NA")
# titre <- "Contros AT vs Calculated AT"
# fit <- lmodel2(data = at_nov_2018_no_NA, AT_filtered_despike ~ at_calc, nperm = 99)
# ggreg2(fit, x = "at_calc", y = "AT_filtered_despike")

@@

### **Calculated / Durafet pHs**
```{r pHs comparaison dur calc, echo=FALSE, message= FALSE, warning=FALSE}
# Normalize phcalc from AT/CT to 4°c
pH_calc <- discrete %>%
  dplyr::select(datetime, sal,temp, phcalc, at)%>%
  dplyr::filter(!is.na(phcalc), !is.na(temp))
pH_calc$pH_calc_norm4 <- pHinsi(pH=pH_calc$phcalc, ALK=pH_calc$at*1e-6, Tinsi=4, Tlab=pH_calc$temp, Pinsi=11, S=pH_calc$sal, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")

@@

# DURAFET vs CALC
fit <- lmodel2(data = d_all,  pH_calc_norm4 ~ pH_durafet_norm4 , nperm = 99)

pdur_calc_norm_text <-  ggplot(d_all,aes(x=pH_durafet_norm4, y= pH_calc_norm4, label = month))+
  geom_text( aes(color=factor(month))) + 
  geom_line(aes(x = pH_calc_norm4, y = pH_calc_norm4), linetype = "dashed") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  labs(title = paste("pH calculated vs pH durafet, normalized at 4°C","\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
   coord_fixed(ratio = 1 , xlim=c(8,8.22), ylim=c(8,8.22)) + 
  scale_color_discrete(guide="none")+
  labs(x="pH durafet, 4°C", y="pH calculated, 4°C ", color = "Months") + theme_bw() 
pdur_calc_norm_text

>>>>

<!-- The slope is: `r #at_slope_TA1` x 3600 x 24 x 365.24 = `r #at_slope1` µmoles.kg-1.yr-1. Regression is: R2 = `r #round(signif(summary(fit)$adj.r.squared, 5), digits =4)`. Outliers are in red. -->

#```{r First period plot, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold', fig.align="center"}
# # Plot of regression
# p <- ggplot(calib_ta_first%>%filter(diff_ta <= 50),aes(datetime,diff_ta)) + 
#     geom_point() + geom_smooth(method='lm', se=FALSE)+ 
#     geom_point(data= calib_ta_first%>%filter(diff_ta >= 50), aes(x=datetime, y=diff_ta), color="red")  +
#   geom_hline(yintercept = 0, linetype="dashed" )+
#   labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
#                      "Intercept =",signif(fit$coef[[1]],5 ),
#                      "Slope =",signif(fit$coef[[2]], 5),
#                      "P =",signif(summary(fit)$coef[2,4], 5))) + 
#   ylab("Difference: Reference - Analyser") + xlab("Time") + scale_x_datetime(date_labels = "%b %Y", date_minor_breaks = "month", timezone="UTC")
# print(p)
# ggsave(paste0("figures/Diff_ref_TA_first_period.png"), p, units="cm")
#```

@@

#```{r Third period, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold',fig.align="center"}

# #remove outliers and remove period without TA measurements 
# calib_ta_third <- d_all%>%
#   dplyr::select(datetime, closest_datetime,AT_filtered, AT_filtered_interp, at,diff_ta, TA_period)%>%
#   dplyr::filter(TA_period == "TA3" & !is.na(at))
# 
# # Parameters of regression
# fit <- lm( data=calib_ta_third, diff_ta ~ datetime)
# at_slope_TA3 <- round(fit$coefficients[[2]] , digits=8)
# at_slope3 <- round(at_slope_TA3 * 3600 *24 * 365.24, digits=2)
# at_intercept3 <- round(fit$coefficients[[1]], digits= 2) # pas besoin ici.
#```

<!--The slope is in days: `r #at_slope_TA3` x 3600 x 24 x 365.24 = `r #at_slope3` µmoles.kg-1.an-1. Regression is: R2 = `r #round(signif(summary(fit)$adj.r.squared, 5), digits =4)`. No outliers.
-->

# ```{r Third period plot, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold', fig.align="center"}
# # # Plot of regression
#  p <- ggplot(calib_ta_third,aes(x=datetime, y=diff_ta) )+ 
#      geom_point() + geom_smooth(method='lm', se=FALSE)+ 
#      #geom_point(data= calib_ta_third%>%filter(diff_ta < -40 & diff_ta<20), aes(x=datetime, y=diff_ta), color="red")  +
#     geom_hline(yintercept = 0, linetype="dashed" )+
#    geom_vline(xintercept = as.POSIXct("2018-01-08 12:55:00", tz="UTC"), colour="red", linetype = "longdash") +
#    #geom_text(aes(xintercept=as.POSIXct("2018-01-01 12:55:00"),label="TA "), colour="red", vjust=1.2)+
#    labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
#                       "Intercept =",signif(fit$coef[[1]],5 ),
#                       " Slope =",signif(fit$coef[[2]], 5),
#                       " P =",signif(summary(fit)$coef[2,4], 5))) + ylab("Difference: Reference - Analyser") + xlab("Time") + 
#    scale_x_datetime( date_labels = "%b %Y", date_minor_breaks = "month", timezone="UTC")
#  print(p)
#  ggsave(paste0("figures/Diff_ref_TA_third_period.png"), p, units="cm")
# ```

@@

# ```{r Second period, echo=FALSE, warning=FALSE, message=FALSE, out.width="100%",fig.show='hold'}

@@

# ```

<!--For the second period, the average difference between 5 discrete samples "references" and TA analyser measurements (`r #mean_offset` µmoles.kg~-1~) was added to TA value as an offset.
-->

#### **Final TA corrected data (Regression)**

<!--The following plot shows the corrected TA data with regressions (Periods 1 and 3) and with offset (Period 2) applied according to Steffen's proposition.
It is clear that these corrected data (in green) cannot be used for periods 1 to 3. The jury is still out for period 4. The issue of salinity must be clarified before an assessment can be made. 
-->

#```{r Correction applied, echo=FALSE, warning=FALSE, message=FALSE, out.width="100%",fig.show='hold'}

@@

#```

@@

<!--In the previous part, missing TA were interpolated with a linear model. This does not reflect the natural variability of TA. For this reason, missing TA is now calculated from salinity data by making a relationship between the same reference TA samples as in the previous part and salinity data.
-->

```{r Discrete salinity vs TA, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%", fig.align="center"}
d_all_at_discrete <- d_all %>% #  To remove an outlier in red
  dplyr::select(datetime, month,closest_datetime, at, sal_fb)%>%
  dplyr::filter( !is.na(at) & !is.na(sal_fb) & sal_fb >30)

  #at != "2307.05" & sal_fb > 28, !is.na(at))

# d_all_Out <- d_all %>% #  To keep an outlier in red
#   filter(at == "2307.05")

#fit <- lm(data = drop_na(d_all_at_discrete, at), at ~ sal_fb)
fit <- lm(data = d_all_at_discrete, at ~ sal_fb)
slope_s_at <- fit$coefficients[[2]]
intercept_s_at <- fit$coefficients[[1]]
# at_s <- ggreg(fit)+ labs(x="Salinity", y="Discrete TA") + Mytheme()

at_s <- ggplot(d_all_at_discrete,aes(x=sal_fb, y= at, label = month))+
  geom_text( aes(color=factor(month))) +
  scale_color_discrete(guide="none")+
    labs(x="Salinity", y="Discrete AT", color = "Months")  +
    stat_smooth(method = "lm", col = "black") +
    labs(title = paste("", "\nAdj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                       ";\nIntercept =",signif(fit$coef[[1]],5 ),
                       ";\nSlope =",signif(fit$coef[[2]], 5),
                       ";\nP =",signif(summary(fit)$coef[2,4], 5))) +
  theme_bw() +
  theme(aspect.ratio=1,
        axis.text=element_text(size=15),
        axis.title.y= element_text(size =15),
        axis.title.x= element_text(size =15),
        plot.margin = unit(c(0.5,1,1,1), "cm"),
        plot.title = element_text(size=15, hjust=0.05,margin = margin(l = 10, b = -70)))
  #print(at_s)

ggsave(paste0("figures/Discrete_TA_salinity_AWIPEV.png"), at_s, width=15, height =11, units="cm")

# Salinity is a predictor of AT -> using the regression defined above
d_all$at_calc <- slope_s_at * d_all$sal_fb + intercept_s_at
```

<!--
The relationship between titrated total alkalinity (references) and salinity is very good with an r2 of `r #round(summary(fit)$r.squared, digits=2)`. Need to compare with other relationships from the literature.
-->

```{r plot Discrete salinity vs TA, echo=FALSE, warning=FALSE, message=FALSE, out.width="60%", fig.align="center"}
 # PLOT
 print(at_s)
```

@@

```{r Plot TA calc TA meas, echo=FALSE, warning=FALSE, message=FALSE,out.width='100%',fig.align='hold'}
at_contros_calc_xts <- dplyr::select(d_all, datetime,at_calc, AT_filtered, at)
at_contros_calc_xts <-  as.xts(at_contros_calc_xts, order.by =d_all$datetime)
dygraph(at_contros_calc_xts, group = "awipev", main="", ylab="Total alkalinity") %>%
  dySeries("AT_filtered", label= "Raw filtered TA", color ="blue", strokeWidth = 0, pointSize=2) %>%
  dySeries("at_calc", label="TA calculated from Salinity",color = RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize=2) %>%
  dySeries("at", label="TA reference",color = "red", strokeWidth = 0, pointSize=4) %>%
  dyEvent(as.POSIXct("2016-05-31 10:00:00", tz="GMT"), "HCl Changed", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2016-06-24 10:00:00", tz="GMT"), "BCG Changed", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2016-02-24 14:00:00", tz="GMT"), "Calibration 1", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2016-09-16 10:00:00", tz="GMT"), "Calibration 2", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2017-03-21 12:00:00", tz="GMT"), "TA analyser changed", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2018-01-08 12:55:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2018-07-31 00:00:00", tz="GMT"), "TA analyser changed #TA-1215-001", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2018-10-30 18:00:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2016-11-15 09:00:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2017-02-09 12:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2017-04-11 06:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2018-01-22 13:00:12", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2018-05-16 12:39:39", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2018-10-31 10:29:27", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2019-01-26 13:25:20", tz="GMT"), "Calibration mode - CRM", labelLoc = "bottom") %>%
  #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
  dyShading(from = TAevents[1], to = TAevents[2], color = "#EDEDED") %>%
  dyShading(from = TAevents[3], to = TAevents[4], color = "#C2C2C2") %>%
  dyShading(from = TAevents[5], to = TAevents[6], color = "#EDEDED") %>%
  dyShading(from = TAevents[7], to = TAevents[8], color = "#C2C2C2") %>%
  dyShading(from = TAevents[9], to = TAevents[10], color = "#EDEDED") %>%
  dyShading(from = TAevents[11], to = TAevents[12], color = "#C2C2C2") %>%
  dyAxis("y",valueRange = c(2000, 2650)) %>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions( strokeWidth= 0) %>%
  dyLegend(show = "follow")   %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE) %>%
    dyRangeSelector(height = 30, dateWindow= NULL)

# #plot for POSTER june 2019
# #plot of TA calculated from S + discrete
# p_at_sal <- ggplot(data = d_all%>%dplyr::filter(at_calc > 2000), aes(x=datetime,y=at_calc,col="TA calculated from salinity") ) +
#   geom_point(col="blue", size=0.5 )+
#   geom_point(aes(y=at, fill= "Discrete measurements"), col="red") +
#   labs(title=  "Calculated from salinity (µmol/kg)", x = "", y= "") + ylim(2100,2350)+
#   theme_bw() + scale_x_datetime(minor_breaks  = "1 month ")+
#   theme(legend.position= c(0.5, 0.93),
#                      legend.text=element_text(size=15),
#                      plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin(t = 9, b = -25)),
#                      axis.text=element_text(size=15),
#                      axis.title.x= element_text(size =15),
#                      legend.title=element_blank())
#
#
# print(p_at_sal)
# ggsave(paste0("figures/poster_at_sal.png"), width= 30, height=10, p_at_sal, units="cm")

@@

#### **TA since November 2018 (final installation)**
```{r TA since November 2018, echo=FALSE, warning=FALSE, message=FALSE,out.width='100%',fig.align='hold'}
 # select subset of data and remove obvious outliers
 at_nov_2018 <-
  dplyr::select(d_all, datetime, at_calc, AT_filtered, at) %>%
  filter(datetime > "2018-11-01", AT_filtered > 2250)
#despike
at_nov_2018 <- mutate(at_nov_2018, AT_filtered_despike = despike(AT_filtered, reference= "median", n=0.5, k=10, replace="NA"))
#plot
at_datetime <- ggplot(data = at_nov_2018, aes(x=datetime)) +
  geom_point(aes(y=AT_filtered, colour = "before"), size =3) +
  geom_point(aes(y=AT_filtered_despike, colour = "after"), size = 2) +
  labs(x = "Time", y = "Total alkalinity", color = "despike")
print(at_datetime)

at_nov_2018_no_NA <- dplyr::filter(at_nov_2018, at_calc != "NA" & AT_filtered_despike != "NA")
titre <- "Contros AT vs Calculated AT"
fit <- lmodel2(data = at_nov_2018_no_NA, AT_filtered_despike ~ at_calc, nperm = 99)
ggreg2(fit, x = "at_calc", y = "AT_filtered_despike")

@@

### **Calculated / Durafet pHs**
```{r pHs comparaison dur calc, echo=FALSE, message= FALSE, warning=FALSE}
# Normalize phcalc from AT/CT to 4°c
pH_calc <- discrete %>%
  dplyr::select(datetime, sal,temp, phcalc, at)%>%
  dplyr::filter(!is.na(phcalc), !is.na(temp), !is.na(sal))
pH_calc$pH_calc_norm4 <- pHinsi(pH=pH_calc$phcalc, ALK=pH_calc$at*1e-6, Tinsi=4, Tlab=pH_calc$temp, Pinsi=11, S=pH_calc$sal, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")

@@

# DURAFET vs CALC
# fit <- lmodel2(data = d_all,  pH_calc_norm4 ~ pH_durafet_norm4 , nperm = 99)
# 
# pdur_calc_norm_text <-  ggplot(d_all,aes(x=pH_durafet_norm4, y= pH_calc_norm4, label = month))+
#   geom_text( aes(color=factor(month))) + 
#   geom_line(aes(x = pH_calc_norm4, y = pH_calc_norm4), linetype = "dashed") +
#   geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
#   labs(title = paste("pH calculated vs pH durafet, normalized at 4°C","\n Adj R2 = ", signif(fit$rsquare, 3),
#                      "; Intercept =", signif(fit$regression.results[2,2], 3),
#                      "; Slope =", signif( fit$regression.results[2,3], 3),
#                      "; P =", signif(fit$P.param, 3))) +
#   theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
#    coord_fixed(ratio = 1 , xlim=c(8,8.22), ylim=c(8,8.22)) + 
#   scale_color_discrete(guide="none")+
#   labs(x="pH durafet, 4°C", y="pH calculated, 4°C ", color = "Months") + theme_bw() 
# pdur_calc_norm_text
